Contextual Combinatorial Cascading Bandits

### 2016-01-15 contextual combinatorial cascading bandits.tex

\begin{figure*}
	\centering
	\subfigure[Disjunctive, $\gamma=1$]{
		\includegraphics[height = 3 cm, width = 5 cm]{synD-1.eps}}
	\subfigure[Disjunctive, $\gamma=0.95$]{
		\includegraphics[height = 3 cm, width = 5 cm]{synD-95.eps}}
	\subfigure[Network 3257 ]{
		\includegraphics[height = 3 cm, width = 5 cm]{network4-1.eps}}
	\subfigure[Conjunctive, network 1755, $\gamma=1$ ]{
		\includegraphics[height = 3 cm, width = 5 cm]{network3B-1.eps}}
	\caption{Synthetic Data Set, L=20, K=4}
	\label{fig:synthetic} % 用于交叉引用
\end{figure*}

>>>>

\begin{figure*}
	\centering
	\subfigure[Disjunctive, $\gamma=1$]{
		\includegraphics[height = 3 cm, width = 4 cm]{synD-1.eps}}
	\subfigure[Disjunctive, $\gamma=0.95$]{
		\includegraphics[height = 3 cm, width = 4 cm]{synD-95.eps}}
	\subfigure[Conjunctive, $\gamma=1$ ]{
		\includegraphics[height = 3 cm, width = 4 cm]{synC-1.eps}}
	\subfigure[Conjunctive, network 1755, $\gamma=1$ ]{
		\includegraphics[height = 3 cm, width = 4 cm]{network3B-1.eps}}
	\caption{Synthetic Data Set, L=20, K=4}
	\label{fig:synthetic} % 用于交叉引用
\end{figure*}
